%-------------------------
% Resume in Latex
% Author : Vedant Arya
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
% \usepackage{charter}

\setlength{\footskip}{4.08003pt}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields

\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \Huge \scshape Vedant Arya \\ \vspace{1pt}
    \small %% xxx-xxx-xxxx $|$ 
    \href{mailto:vedant.arya.0x80@proton.me}{\underline{vedant.arya.0x80@proton.me}} $|$ 
    \href{https://linkedin.com/in/vavava0x80}{\underline{linkedin.com/in/vavava0x80}} $|$
    \href{https://github.com/martian0x80}{\underline{github.com/martian0x80}} $|$
    Delhi, IN
\end{center}


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, C\#/.NET, Go, Shell Scripting (bash/zsh)} \\
     \textbf{Frameworks}{: ASP.NET Core, Entity Framework Core, Dapper, Flask, SQLAlchemy Core, Django Rest Framework, OpenTelemetry} \\
     \textbf{Developer Tools}{: Git, Jetbrains, SQL (Postgres, MySQL), NoSQL (Redis), Docker, Traefik, Prometheus, Grafana} \\
     \textbf{Cloud}{: Azure Web Apps, Azure VM, AWS EC2}
    }}
 \end{itemize}
%----------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {\textbf{IPUSenpai} $|$ \emph{ASP.NET, Python, ETL, Docker, Postgresql, Redis, Prometheus} $|$ \href{https://github.com/martian0x80/IPUSenpaiBackend}{\color{blue}\underline{Github}} $|$ \href{https://devel.ipusenpai.in}{\color{blue}\underline{ipusenpai.in}}}{March 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a data analytics app to provide a statistical dashboard and ranklist from results published by IPU.}
            \resumeItem{Results published by IPU were in an obscure format and challenging to parse and analyze, lacking significant statistical data.}
            \resumeItem{As a result:
              \begin{itemize}
                \item Built a robust multiprocessing parser using complex regex patterns. Designed and implemented a scalable ETL pipeline using Python (SQLAlchemy) for automated data parsing, transformation, and loading.
                \item Constructed a high-performance REST API with ASP.NET Core and Entity Framework Core, later migrating to Dapper for further performance gains.
                \item Carefully crafted a beautiful UI interface with Next.js, TypeScript, and Tailwind CSS.
                \item Implemented a CI/CD pipeline using Docker, DockerHub Registry, and GitHub Actions for automated Web API deployments.
              \end{itemize}
            }
            \resumeItem{Gained \textbf{2.2K+} users and \textbf{12K+} views within the first week of launch.}
            % \resumeItem{Implemented a CI/CD pipeline using Docker, DockerHub Registry, and GitHub Actions for automated Web API deployments.}
            \resumeItem{Utilized Traefik for reverse proxy and load balancing. Used OpenTelemetry, Prometheus and Grafana stack for monitoring and observability.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Dotnotes} $|$ \emph{Flask, Python, DriveV3 API, Shell scripting, Spider, Git} $|$ \href{https://www.dotnotes.xyz/}{\color{blue}\underline{dotnotes.xyz}}}{October 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Conceptualized and implemented Dotnotes, a platform for seamless sharing of B.Tech course materials.}
            \resumeItem{Need for an efficient way to share and access course materials.}
            \resumeItem{Developed a backend API in Flask, deployed on Azure, and integrated Redis for caching.}
            \resumeItem{Achieved \textbf{150K+} pageviews and \textbf{7.5K+} users within the first 90 days.}
            \resumeItem{Led a team to build, improve, and scale the platform.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{PureAES} $|$ \emph{C, FIPS-197} $|$ \href{https://github.com/martian0x80/PureAES}{\color{blue}\underline{Github}}}{March 2023 -- April 2023}
          \resumeItemListStart
            \resumeItem{Implemented the Advanced Encryption Standard (AES) symmetric key block cipher in pure C.}
            \resumeItem{Need for a minimal AES implementation without external dependencies.}
            \resumeItem{Developed based on FIPS-197, supporting 128, 192, and 256-bit key sizes.}
            \resumeItem{Successfully tested against NIST test vectors, ensuring compliance and reliability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {GGSIPU University $|$ \emph{$8.68$ CGPA}}{Delhi, India}
      {Bachelor of Technology in Computer Science}{Nov. 2022 -- Nov. 2026}
  \resumeSubHeadingListEnd


%-----------ACCOMPLISHMENTS-----------
\section{Accomplishments}
    \resumeSubHeadingListStart
        \resumeSubheading
            {buildspace s5 - Grant Awardee}{June 2024}
            {buildspace s5}{}
            \resumeItemListStart
                \resumeItem{Won a \$$100$ grant to build and launch my idea at buildspace s5}
            \resumeItemListEnd
    
        \resumeSubheading
            {Google Solution Challenge 2024 - Global Top 100 Finalist}{December 2023}
            {Google Developer Student Clubs - Google $|$ \href{https://developers.google.com/community/gdsc-solution-challenge/winners}{\color{blue}\underline{Winners}} $|$ \href{https://drive.google.com/file/d/1ZjR0Lc5kgL_BWWEfPina2izSWEeD0eaM/view?usp=sharing}{\color{blue}\underline{Certificate}}}{}
            \resumeItemListStart
                \resumeItem{Developed a platform that connects individuals seeking short-term, informal jobs (e.g., gardening, moving assistance) with local opportunities}
                \resumeItem{Developed a backend API with Django Rest Framework along with JWT (JSON Web Token) authentication}
                \resumeItem{Prepared a CRUD API endpoint to create new jobs from the frontend}
            \resumeItemListEnd

        \resumeSubheading
            {Prize Pool Category - 2nd Place}{March 2023}
            {Live The Code: 2.0 $|$ \href{https://verification.givemycertificate.com/v/e39f804d-d1d3-4bcc-acaf-4d0ce8873540}{\color{blue}\underline{Verify}}}{}
            \resumeItemListStart
                \resumeItem{Built a health chatbot solution "Medimate" using open source LLaMa models}
                \resumeItem{Implemented a backend API with Flask to fetch LLM's responses}
                \resumeItem{Used IPT (Instruction Prompt Tuning) to guide LLM responses}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

% \section{Interests}
    

%-------------------------------------------
\end{document}
